Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-05-29 Manuscript.Rmd
final corrplot fixed

# corrplot(mixSummary$Betas, 
#          is.corr = F, 
#          p.mat = mixSummary$Pvals, 
#          type = "lower",
#          outline = T,
#          insig = "label_sig",
#          sig.level = c(.001, .01, .05),
#          pch.col = "white",
#          na.label = "square", 
#          na.label.col = "grey",
#          method = "color", 
#          tl.col = "black",
#          tl.cex = 0.8,
#          cl.length = 5,
#          cl.lim = c(-2.0001, 2.0001),
#          col = col2(200))

>>>>

# corrplot(mixSummary_wth$Betas,
#          is.corr = F,
#          p.mat = mixSummary_wth$Pvals,
#          type = "lower",
#          outline = T,
#          insig = "label_sig",
#          sig.level = c(.001, .01, .05),
#          pch.col = "white",
#          na.label = "square",
#          na.label.col = "grey",
#          method = "color",
#          tl.col = "black",
#          tl.cex = 0.8,
#          cl.length = 5,
#          col = col2(200))
